### 2018-09-28 ms.tex
Move tables.
First pass at discussion.

Here we formulate a joint model that combines aggregated surveillance data and point prevalence-surveys of \emph{Plasmodium falciparum}.
The model has seperate likelihoods for the two data types.
We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We compare the joint model to two benchmark models, a prevalence-survey only model and an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless}.
As case studies we use data from Indonesia, Senegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.

@@

We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
For Indonesia we selected 2012 for surveillance data (380 regions) and 2010 for  prevalence data (969 surveys, 128537 individuals).
For Senegal we selected 2015 for both surveillance data (46 regions) and prevalence data (216 surveys, 8114). % update todo
Finally, for Madagascar we selected 2013 for both surveillance (110 regions) and prevalence (290 surveys, 7244 individuals) data.

@@

The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
As the prevalence surveys cover different age ranges they were standardised using the model from \cite{smith2007standardizing}.

@@

We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only prevalence data and 3) the submodel with only aggregated incidence data. 
The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}

@@

Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of 3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularised our model.

@@

In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
Our main performance metric was mean absolute error (MAE) for incidence and MAE weighted by survey sample size for prevalence.
While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
As the models are being fitted on data on difference scales we found that predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
% Why not correlation
To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.

@@

@@

@@

The polygon-only model and the joint model seem to be fairly well calibrated.
The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.65 and 0.85.
The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
The points only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial crossvalidation in Madagascar.

@@

\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/idn_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia. The values plotted for areas with no polygon data are the means across all cross-validation folds.
}
\label{predobsmapidn}
\end{figure}

\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/sen_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
}
\label{predobsmapsen}
\end{figure}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for random crossvalidation experiment.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Indonesia & 18.33 & {\bf 14.02} &  14.09\\
& Senegal & 51.24 & {\bf 26.74} &  28.45\\
& Madagascar & 85.54 & 37.45 &  {\bf 34.49}\vspace{3mm}\\
Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
& Senegal & {\bf 0.015} & 0.024 &  0.024\\
& Madagascar & {\bf 0.054} & 0.059 &  0.059\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
The data were split randomly into 10 groups stratified by data type (incidence polygon and prevalence points).
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for spatial crossvalidation experiment.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Indonesia &  18.13 &  {\bf 14.77} &   15.02\\
& Senegal &  51.17 &  41.43 &   {\bf 36.76}\\
& Madagascar & 107.32 &  71.44 &   {\bf 65.50}\vspace{3mm}\\
Prevalence & Indonesia & 0.011 & {\bf 0.010} &  {\bf 0.010}\\
& Senegal & {\bf 0.015} & 0.019 &  0.019\\
& Madagascar & 0.069 & 0.066 &  {\bf 0.065}\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
The data were split spatially into 7 groups (Indonesia.
\end{flushleft}
\label{table2}
\end{adjustwidth}
\end{table}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
}
\label{randompredobsscatter}
\end{figure}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!h]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
}
\label{spatialpredobsscatter}
\end{figure}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals for.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Crossvalidation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
&& Senegal & 0.11 & 0.80 &  0.85\\
&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
&& Senegal & 0.30 & 0.67 &  0.70\\
&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
&& Senegal & 0.80 & 0.71 &  0.91\\
&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
&& Senegal & 0.90 & 0.88 &  0.79\\
&& Madagascar & 0.93 & 0.68 &  0.83\\
\end{tabular}
\begin{flushleft}

@@

@@

% Short comings

% Future work

% Temporal model

% nonlinearities

% Relative amaounts of data

% Geographies.

% Data size. In spat inc, countries with few polys improve. In random madagascar improves.
% Senegal points mostly zero. MAtters?

% Clear benefits, when some areas have polygon and some have PR.

>>>>

Here we formulate a joint model that combines aggregated surveillance data and point prevalence-surveys of \emph{Plasmodium falciparum}.
The model has seperate likelihoods for the two data types.
We relate the two malariometric measures by using a previously estimated relationship within the model \cite{cameron2015defining}.
We compare the joint model to an aggregated-incidence disaggregation model similar to previous models \cite{sturrock2014fine, wilson2017pointless} and a further benchmark model that contains on;y prevalence-survey data.
As case studies we use data from Indonesia, Senegal and Madagascar as these countries have both good routine surveillance data and good coverage of prevalence point surveys.

@@

We used two data sources that reflect malaria burden; point prevalence surveys and polygon-level, aggregated incidence data.
We selected Indonesia, Senegal and Madagascar as case examples as they all have good surveillance data and good country wide surveys from approximately the same time.
To minimise temporal effects we select, for each country, one year of prevalence survey data and one year of surveillance data.
For Indonesia we selected 2012 for surveillance data (380 regions) and 2010 for  prevalence data (969 surveys, 128,537 individuals).
For Senegal we selected 2015 for both surveillance data (46 regions) and prevalence data (216 surveys, 8,114). % update todo
Finally, for Madagascar we selected 2013 for both surveillance (110 regions) and prevalence (290 surveys, 7,244 individuals) data.

@@

The prevalence survey data were extracted from the Malaria Atlas Project prevalence survey database \cite{bhatt2015effect}.
As the prevalence surveys cover different age ranges they were standardised to an age-range of 2--10 using the model from \cite{smith2007standardizing}.

@@

We compared three models 1) a full model with prevalence surveys and aggregated incidence data 2) the submodel with only aggregated incidence data and 3) the benchmark submodel with only prevalence point-survey data. 
The models were implemented and fitted using Template Model Builder \cite{TMB} in R \cite{R}

@@

Finally, we set regularising priors on the regression coefficients $\beta_i \sim \operatorname{Norm}(0, 0.04)$. 
Given the standardised covariates, a regression coefficient from the 95\% IQR of this distribution, and an intercept of -3, each covariate would be able to predict prevalences between 0.004 and 0.27. 
This prior encodes our belief that the full range of malaria transmission can not be explained by a single covariate and our desire to regularise our model.
This regularisation is particularly important given the small number of observations in Senegal (n = 46) and Madagascar (n = 110).

@@

In both cases we examined performance metrics for both the withheld prevalence data and the withheld incidence data.
As there is no good way of combining predictive error from both types of data into one performance metric, we considered performance separately throughout.
We considered the ability to predict incidence correctly out main objective.
However, a problem with using polygon data in a cross-validation scheme is that a model can perform well at the polygon level but not correctly predict the pixel-level malaria risk.
Predictive performance on prevalence points is one way to measure how well a model can predict pixel-level malaria risk.
However, in areas of low prevalence, small or moderately sized prevalence surveys can be noisey or unsensitive and so care must be taken when interpreting predictive performance on these data.
Our main performance metric was mean absolute error (MAE) for incidence and MAE weighted by survey sample size for prevalence.
While other metrics could have been used, we specifically did not use correlation as correlation measures linear dependance without regard to slope or intercept.
As the models are being fitted on data on difference scales we found that predictions were sometimes correlated but strongly displaced from the one-one line and therefore correlation metrics were misleading.
% Why not correlation
To assess how well the models were calibrated we considered coverage of the 80\% predictive credible intervals on the hold-out data.

@@

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for random cross-validation experiment.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Indonesia & 18.33 & {\bf 14.02} &  14.09\\
& Senegal & 51.24 & {\bf 26.74} &  28.45\\
& Madagascar & 85.54 & 37.45 &  {\bf 34.49}\vspace{3mm}\\
Prevalence & Indonesia & 0.010 & 0.010 &  0.010\\
& Senegal & {\bf 0.015} & 0.024 &  0.024\\
& Madagascar & {\bf 0.054} & 0.059 &  0.059\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
The data were split randomly into 10 groups stratified by data type (incidence polygon and prevalence points).
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of out-of-sample accuracy for spatial cross-validation experiment.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Indonesia &  18.13 &  {\bf 14.77} &   15.02\\
& Senegal &  51.17 &  41.43 &   {\bf 36.76}\\
& Madagascar & 107.32 &  71.44 &   {\bf 65.50}\vspace{3mm}\\
Prevalence & Indonesia & 0.011 & {\bf 0.010} &  {\bf 0.010}\\
& Senegal & {\bf 0.015} & 0.019 &  0.019\\
& Madagascar & 0.069 & 0.066 &  {\bf 0.065}\\
\end{tabular}
\begin{flushleft}
Mean absolute error of predicted incidence rate and weighted mean absolute error of prevalence against out-of-sample observed data for three countries.
The data were split into seven, four and three groups in Indonesia, Senegal and Madagascar respectively.
\end{flushleft}
\label{table2}
\end{adjustwidth}
\end{table}

@@

% Further results. Accuracy or recall of Sen. Correlation for some?

@@

The polygon-only model and the joint model seem to be fairly well calibrated (Table~\ref{table3}).
The proportion of out-of-sample incidence datapoints being within their 80\% credible intervals ranged between 0.65 and 0.85.
The proportion of out-of-sample prevalence datapoints being within their 80\% credible intervals ranged from 0.50 to 0.96.
The points only model was reasonably well calibrated for predictions of prevalence (coverage ranging from 0.8 to 0.93) but was poorly calibrated for predicting incidence with coverage values as low as 0.11 and the best coverage value being 0.68 for spatial cross-validation in Madagascar.
With respect to uncertainty in incidence predictions, the polygon-only model and joint model were similar; adding the points sometimes improved coverage and sometimes made it worse.
However, with respect to uncertainty in prevalence predictions, the coverage was substantially improved in three of six cases and marginally improved in one case.
Coverage improved in the random cross-validation in Indonesia (polygon-only 0.50, joint 0.80) and Madagascar (polygon-only 0.53, joint 0.74) and spatial cross-validation in Madagascar (polygon-only 0.68, joint 0.83) and marginally improved in the spatial cross-validation in Senegal (polygon-only 0.88, joint 0.79).
In the remaining two cases, adding points did not substantially improve coverage, but did make the model more conservative, with coverage of 0.91 rather than 0.71 in the random cross-validation Senegal experiment and 0.96 instead of 0.62 in the spatial cross-validation Indonesia experiment.

@@

\begin{figure}[!t]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/idn_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data (top), predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Indonesia. The values plotted for areas with no polygon data are the means across all cross-validation folds.
}
\label{predobsmapidn}
\end{figure}

\begin{figure}[!t]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/sen_both_cv12_preds.png}
\caption{{\bf Input incidence data and predicted incidence maps. } 
The incidence (log10) data, predicted log10 incidence from the joint model for randomly sampled out-of-sample polygons (middle) and predicted log10 incidence from the joint model for spatially sampled out-of-sample polygons (bottom) for Senegal.
}
\label{predobsmapsen}
\end{figure}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!t]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/random_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for random cross-validation experiments.}
A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
}
\label{randompredobsscatter}
\end{figure}

%figure 5, 6. Spat and random cv. PR vs Poly columns, countries as rows, model as colour?
\begin{figure}[!t]
% to be removed before submission
\includegraphics[width = 0.9\textwidth]{figures/spatial_cv_scatter.pdf} %\caption{Indonesia spatial crossvalidation} 
\caption{{\bf Observed-predicted plots for spatial cross-validation experiments.}
A-B) Indonesia, C-D) Senegal, E-F) Madagascar. A, C, E) square root aggregated incidence (per 1,000), B, D, F) square root prevalence.
Results from all three models are included with the points only model being shown in orange, the downscaling model being shown in blue and the combined model being shown in green.
}
\label{spatialpredobsscatter}
\end{figure}

\begin{table}[!t]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{
{\bf Summary of coverage of 80\% credible intervals for.}}
\begin{tabular}{llllll}
\hline
{\bf Holdout data} & {\bf Cross-validation} & {\bf Country} &  {\bf Points} & {\bf Polygons} & {\bf Joint} \\
\thickhline 
Incidence & Random & Indonesia & 0.13 & 0.72 &  0.73\\
&& Senegal & 0.11 & 0.80 &  0.85\\
&& Madagascar & 0.59 & 0.82 &  0.77\vspace{1mm}\\
& Spatial & Indonesia & 0.14 & 0.76 &  0.68\\
&& Senegal & 0.30 & 0.67 &  0.70\\
&& Madagascar & 0.68 & 0.65 &  0.68\vspace{3mm} \\
Prevalence & Random & Indonesia & 0.90 & 0.50 &  0.80\\
&& Senegal & 0.80 & 0.71 &  0.91\\
&& Madagascar & 0.83 & 0.53 &  0.74\vspace{1mm}\\
& Spatial & Indonesia & 0.87 & 0.62 &  0.96\\
&& Senegal & 0.90 & 0.88 &  0.79\\
&& Madagascar & 0.93 & 0.68 &  0.83\\
\end{tabular}
\begin{flushleft}

@@

We have compared the predictive performance of a disaggration model and a model that jointly learns from aggregated incidence data and point prevalence surveys.
With regards to a random cross-validation scheme, adding points to the disaggregation model improved performance in one of three countries (Madagascar).
With regards to a spatial cross-validation scheme, which tests a models ability to predict malaria risk far away from available data, we found that adding the point surveys improved the disaggregation models in both Senegal and Madagascar.

A problem with using cross-validation on polygon data is that models can correctly predict polygon-level incidence while incorrectly predicting the within-polygon, pixel-level risk.
Of the four cases where polygon predictions were improved or similar (Indonesia and Madagascar random cross-validation and Senegal and Madagascar spatial cross validation) the predictive performance on prevalence points was always unchanged or marginally improved.
However, the points only model was the top or equal top model at predicting point level prevalence in four out of six cases and only marginally worse in one further case.
Only in the Madagascar, spatial cross-validation experiment was the points-only model notably worse at predicting prevalence.

@@

The joint model improved the prediction of incidence in two of three countries under the spatial cross-validation scheme but only one country in the random cross-validation scheme.
Furthermore, in the spatial cross-validation scheme, the two countries where performance was improved by using the joint model are the two countries with the least data.
The joint model seems to be helping in the cases where predictions have little information from the random field and when there is little data to estimate regression parameters.
In contrast, the joint model does not in general improve on the polygon-only model in the random cross-validation scheme.
A noticable element of this scheme was that locations where polygon data was removed for validation could still potentially have prevalence data.
Figure~\ref{fig:cv_random} implies that this situation is the norm.
Yes this spatial information did not improve performance in Indonesia or Senegal.

% Clear benefits, when some areas have polygon and some have PR.
%   Where?

There are large potential benefits to models that combine data in the context of large scale studies over multiple countries.
In these cases there is often different data types in different countries and being able to make malaria estimates of the countries together increases spatial coverage and statistical power.
Further cases where this joint model may be particularly beneficial is in countries where prevalence surveys are strongly clustered in one area --- typically an area of high malaria risk --- but without high resolution surveillance data. 
In these regions, fitting a model on just the points requires predictions far away from the survey locations whlie fitting a model just on the surveillance data will be underpowered.

However, the benefits of these methods do not come for free, as indicated by the reduced performance in some cases.
Two main aspects of prevalence point data have the potential to reduce the predictive ability of a polygon-only model.
Firstly, the data are on a difference scale.
Here we have used a previously fitted model \cite{cameron2015defining} in order to be able to fit the joint model.
However, this model is imperfect in that it is calibrated with a relatively small amount of matched prevalence and incidence data.
Furthermore the true relationship between prevalence and incidence is likely to vary spatially as aspects such as immunity, nutrition and health care will be different.
In using a joint model we are accepting these failings in the hope that the benefits of including additional data are stronger than the costs of using mismatched data.
The second aspect of prevalence point data that could reduce the predictive ability of a polygon-only model by adding point data is if the point data is of low quality.
In particular, non-random sampling of individuals can produce biased estimates of prevalence and this will decrease model performance.
In countries with lots of high quality, high resolution incidence data, the potential benefits of including point data in the model are reduced while the potential costs remain.

For a model to be robust to shortcomings in the prevalence-incidence relationship from \cite{cameron2015defining}, future models could be more flexible in the way they use this relationship.
This could be by estimating the parameters of the polynomial jointly with the rest of the model.
Informative priors based on the original model should be used to regularise this joint fit both to prevent unbelievable inferences but also because if the relationship is too flexible, the information from the prevalence data might not be used by the incidence level model.
This is particularly true for even more flexible model forms that could be used such as a spline or a Gaussian process on the relationship between prevalence and incidence.

For the model to handle noisey or biased prevalence data points, the modeller can control the iid random effect on the point surveys, $w_i$. 
Here we have tried to maximise the influence of the prevalence data by setting the prior based on the belief that the random effect should only explain extra-binomial variation that is impossible to explain with the covariates (i.e. based on the differences in prevalence surveys within the same pixel).
Weakening this prior will allow the iid effect to explain more of the point survey variation which both reduces the potential statistical power gained by adding the point data but also reduces the effects of biased or noisey estimates.

In order to specifically compare the affects of combining the data types, we have aimed to keep the models fitted here as simple as possible.
However, a number of improvements could be made.
Data from multiple years are available for many countries.
Simply combining data collected at different times is not recommended as malaria incidence is changing rapidly.
However, fitting a full spatio-temporal model would be a suitable way to combine data from different periods but would be computationally more expensive.
This is an avenue of work that should be pursued.
Furthermore, it has been clearly established that simple linear combinations of environmental covariates cannot fully explain malaria risk \cite{bhatt2017improved}.
A number of methods could be used to include non-linear effects of covariates and interactions into the model.
Firstly, as in \cite{bhatt2017improved}, machine learning models could be fitted to the prevalence data and then predictions from these models could be used as covariates in the full model.
This approach is feasible but does not allow any information from the polygons to inform non-linear relationships.
To directly model non-linear effects in the full model could be achieved by including simple non-linear functions such as splines, though the increased model complexity would require more data than was used in Senegal and Madagascar in this study.
Finally, Gaussian process regression, with smoothly varying effects in environmental and geographic space could be used \cite{law2018variational}.
These are computational expensive without careful approximations via variational Bayes or other approximations.
Again these models need a lot of data and careful regularisation for good predictive performance.
